Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-07 Latex/journal_v1/V5/pr.tex
finish analyse journal1
add code

Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
\end{split}
\end{equation}
Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}+\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (\kappa^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{F}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
      0 & \text{otherwise}
    \end{cases}
\end{equation}
\end{lemma}
Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
The complexity order of this problem is about $O(\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

 The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is based on the distance, channel quality, and the fronthaul capacity. Also, the number of activated VNF for each slice is obtained from the simulation. 
The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}. In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels, the fronthaul capacity, and channel distance.

>>>>

Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
\end{split}
\end{equation}
Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
      0 & \text{otherwise}
    \end{cases}
\end{equation}
Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{lemma}
Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
The complexity order of this problem is about $O(\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

 The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on the distance. Also, the number of activated VNF for each slice is fixed. 
The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}. In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
